\documentclass[12pt]{article}
\usepackage{titling}
\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage[bottom]{footmisc}
\usepackage{float}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{colorlinks=true, %Colours links instead of ugly boxes
urlcolor=red, %Colour for external hyperlinks
linkcolor=blue, %Colour of internal links
citecolor=blue %Colour of citations
}
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage[english]{babel}
\usepackage[margin=1in,includefoot]{geometry}



\setlength\parindent{0pt}

\pagestyle{fancy}
\fancyhf{}
\rhead{Syed Waleed Mehmood Wasti}
\lhead{DScourseS21 - PS 4}
\cfoot{\thepage}



\title{\textbf{Data Science for Economists - Spring 21 \\
\vspace{0.5cm}
Problem Set 4}}
\author{Syed Waleed Mehmood Wasti}
\date{\today}


\begin{document}

\begin{titlepage}
\maketitle
\thispagestyle{empty}
\end{titlepage}



\textbf{Q7.} I am interested in finding out how the engagement level of a certain tweet of an individual impacts his/her subsequent tweet. So basically if a person tweets and gets a good response on it in terms of the likes and comments then how likely is he/she to tweet sooner rather than later. Also is the subsequent tweet likely to be on a similar topic or something very diverse. \\\\


\textbf{Practice with JSON files (R exercise part 1)}
  
\begin{enumerate}[label=\alph*]
  \item N/A
  \item N/A
  \item N/A
  \item Ans: mydf is:  [1] ``tbl\_df"     ``tbl"        ``data.frame"\\
   mydf\$date is [1] ``character"
  \item
  
  First 10 rows: Command= head(mydf,10); \\ 
Result = # A tibble: 10 x 6 \\
date  description                       lang  category1 category2 granularity \\
$<$chr$>$ $<$chr$>$                             $<$chr$>$ $<$chr$>$    $<$chr$>$     $<$chr$>$ \\
1 1     Tiberius, under order of Augustu… en    By place  Roman Em… year \\
2 1     Gaius Caesar and Lucius Aemilius… en    By place  Roman Em… year \\
3 1     Gaius Caesar marries Livilla, da… en    By place  Roman Em… year \\
4 1     Quirinius becomes a chief adviso… en    By place  Roman Em… year \\
5 1     Areius Paianeius becomes Archon … en    By place  Roman Em… year \\
6 1     The ''Yuanshi'' era of the Chine… en    By place  Asia      year \\
7 1     Confucius is given his first roy… en    By place  Asia      year \\
8 1     Emperor Ping of Han China begins… en    By place  Asia      year \\
9 1     Former regent Dong Xian commits … en    By place  Asia      year \\
10 1     Sapadbizes, Yuezhi prince and Ki… en    By place  Asia      year \\


  
  
\end{enumerate}





\textbf{Practice with sparklyr (R Exercise part 2)}

\begin{enumerate}
    \item N/A 
    \item N/A
    \item N/A
    \item N/A
    \item N/A
    \item N/A
    \item 
    class(df1) is: [1] ``tbl\_df"     ``tbl"        ``data.frame" \\
    class(df) is: [1] ``tbl\_spark" ``tbl\_sql"   ``tbl\_lazy"  ``tbl" \\
    
    Yes. They are both different. 
    
    \item Yes, the column names are different. 
    \item 
    \begin{enumerate}
        \item   Sepal\_Length Species \\
         $<$dbl$>$ $<$chr$>$ \\ 
1          5.1 setosa \\
 2         4.9 setosa \\
  3        4.7 setosa \\ 
   4       4.6 setosa \\
    5      5   setosa \\ 
     6     5.4 setosa \\
    \end{enumerate}
    \item 
    \begin{enumerate}
        \item 
         Source: spark$<$?$>$ [?? x 5]
  Sepal\_Length Sepal\_Width Petal\_Length Petal\_Width Species \\
         $<$dbl$>$       $<$dbl$>$        $<$dbl$>$       $<$dbl$>$ $<$chr$>$ \\
1          5.8         4            1.2         0.2 setosa \\
2          5.7         4.4          1.5         0.4 setosa \\
3          5.7         3.8          1.7         0.3 setosa \\
4          7           3.2          4.7         1.4 versicolor \\
5          6.4         3.2          4.5         1.5 versicolor \\
6          6.9         3.1          4.9         1.5 versicolor\\

    \end{enumerate}
    \item
    # Source: spark$<$?$>$ [?? x 2]\\
  Sepal\_Length Species\\
         $<$dbl$>$ $<$chr$>$\\
1          5.8 setosa \\
2          5.7 setosa \\
3          5.7 setosa \\
4          7   versicolor \\
5          6.4 versicolor \\
6          6.9 versicolor \\
    \item  
    # Source: spark$<$?$>$ [?? x 3] \\
  Species     mean count \\
  $<$chr$>$     $<$dbl$>$ $<$dbl$>$ \\
1 virginica   6.59    50 \\
2 versicolor  5.94    50 \\
3 setosa      5.01    50 \\
    \item
    \begin{enumerate}
        \item 
     Source: spark$<$?$>$ [?? x 3] \\
  Species     mean count \\
  $<$chr$>$     $<$dbl$>$ $<$dbl$>$ \\
1 virginica   6.59    50 \\
2 versicolor  5.94    50 \\
3 setosa      5.01    50 \\
        \item
             Species  mean count \\
1     setosa 5.006    50 \\
2 versicolor 5.936    50 \\ 
3  virginica 6.588    50 \\
    \end{enumerate}
    
    
\end{enumerate}
\end{document}
