\documentclass[12pt]{article}
\usepackage{titling}
\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage[bottom]{footmisc}
\usepackage{float}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{colorlinks=true, %Colours links instead of ugly boxes
urlcolor=red, %Colour for external hyperlinks
linkcolor=blue, %Colour of internal links
citecolor=blue %Colour of citations
}
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage[english]{babel}
\usepackage[margin=1in,includefoot]{geometry}



\setlength\parindent{0pt}

\pagestyle{fancy}
\fancyhf{}
\rhead{Syed Waleed Mehmood Wasti}
\lhead{DS21 - PS 1}
\cfoot{\thepage}



\title{\textbf{Data Science for Economists}}
\author{Syed Waleed Mehmood Wasti}
\date{\today}


\begin{document}


\maketitle

\section*{Introduction}

I am particularly interested in the development field of Economics because of my interest in poverty and entrepreneurship. This area interests me because I plan to come up with policies to reduce poverty in my home country once I am done with my degree program. I am interested in taking this class because ever since I started using \LaTeX\, I was quite intrigued and looked up ways in which I could document stuff. This opened me to the world of Markdown and Vim and created an interest in me to learn about these things. Furthermore, just like we discussed in this course, automating makes us more productive in the long-run, I believe this course would really help me achieve that level of automation where I am able to accomplish more and in an organized manner. I am extremely interested in using Vim and tried completing the Vimtutor which was a lot of fun! I am still not sure what I would do in the project for this class but if I am able to work on a project related to poverty then that would be great. I plan to learn the basics of R in this course and take it from there, learn more of it by myself and use it in my research. After graduation, I plan to rejoin academia; passing on what I have learnt to my students and contributing to the betterment of my country through research. \\

\section*{Equation} 

\begin{equation}
    a^2 + b^2 = c^2
\end{equation}






\end{document}
